### 2018-06-12 dissemination.publication/request-asplos18-front-matter/paper.tex
minor fixes

Since collapsing all metrics into one to select a single
winner often results in over-engineered solutions, we have
opted instead to select multiple implementations from
a Pareto-frontier, based on their uniqueness or simply
to obtain a reference implementation. The authors of such
selected solutions were given an opportunity to share their
insights at the associated \href{http://cknowledge.org/request-cfp-asplos2018.html}{ReQuEST workshop} 
co-located with the 23rd ACM ASPLOS conference at the end of March 2018
in Williamsburg, VA, USA.

@@

Most importantly, the community can now access all the above
CK workflows under permissive licenses and continue
collaborating on them via dedicated 
\href{https://github.com/ctuning/ck-request-asplos18-results}{ReQuEST'18 GitHub projects}. 
First, the workflows can be automatically \href{https://github.com/ctuning/ck/wiki/Portable-workflows}{adapted}
to new platforms and environments by either detecting already
installed dependencies (e.g. libraries) or rebuilding
dependencies via an integrated \href{http://cKnowledge.org/shared-packages.html}{package manager} supporting
Linux, Windows, MacOS and Android. Second, the workflows can
be customized by swapping in new models, data sets,
frameworks, libraries, and so on. Third, the workflows can be
extended to expose new design and optimization choices (e.g.
quantization), as well as evaluation metrics (e.g. power
or memory consumption). Finally, the workflows can be used for
collaborative autotuning ("\href{http://cKnowledge.org/rpi-crowd-tuning}{crowd-tuning}") 
to explore huge optimization spaces using devices such as 
\href{https://play.google.com/store/apps/details?id=openscience.crowdsource.video.experiments}{Android phones and tablets}, 
with best solutions being made available to the
community on the \href{http://cKnowledge.org/dnn-crowd-benchmarking-results}{online CK scoreboard}.

@@

Fair competitive benchmarking between different platforms,
frameworks and models is hard work. It requires carefully
considering model equivalence (e.g. performing the same mix of
operations), input equivalence (e.g. preprocessing the inputs
in the same way), output equivalence (e.g. validating the
outputs for each input, not just calculating the usual
aggregate accuracy score), etc. Formalizing the benchmarking
requirements and encapsulating them in shared CK components
(e.g. using a framework-independent model representation such
as \href{https://onnx.ai/}{ONNX}) and workflows (e.g. for input conversion and output
validation), should help standardize and automate the
benchmarking process.

@@

\begin{center}\includegraphics{ck-assets/artifacts_automated_dl.jpg}\end{center}

@@

Artifact evaluation may require access to expensive
computational resources (e.g. cloud instances with 72-core
servers), proprietary tools (e.g. Intel compilers), and
auxiliary hardware (e.g. power meters). Raising the profile
of AE by widely recognizing its benefits and impact should
help us obtain access, licensees and sponsorship from the
industry and funding agencies.

@@

Full experimental evaluation can take many weeks (for example,
when validating accuracy on 50,000 images on a 100 MHz FPGA
board). The AE committee can collaborate with the authors
to determine a minimally useful scope for evaluation which
would still provide insights to the community. The community
can eventually crowdsource full evaluation. In other words,
AE can be "staged" with a quick check that the artifacts are
"functional" before the camera-ready deadline followed by full
evaluation using the ReQuEST methodology. In fact, ReQuEST can
grow into a non-profit service to conferences and journals.
Sponsorship should help attract experienced full-time
evaluators, as well as part-time volunteers to work
on unifying and evaluating artifacts and workflows.

@@

\item collaborating with the community, our Advisory Board and ACM to address the above issues;
\item using the ReQuEST experience to assist AE at the upcoming \href{http://sysml.cc}{SysML'19} conference;
\item replacing non-representative benchmarks with realistic workloads;
\item creating realistic training sets based on mispredictions shared by the community;
\item improving the benchmarking and co-design methodology, and contributing to emerging benchmarking initiatives such as \href{http://mlperf.org}{MLPerf};
\item collaborating with other competitions such as \href{https://rebootingcomputing.ieee.org/lpirc}{LPIRC}, \href{https://dawn.cs.stanford.edu/benchmark}{DAWNBench} and \href{https://sc18.supercomputing.org/experience/studentssc/student-cluster-competition}{SCC} on developing a common experimental framework;
\item standardizing \href{http://cKnowledge.org/rpi-crowd-tuning}{multi-objective autotuning and co-design workflows};
\item improving and documenting the experimental framework and scoreboard;
\item generating reproducible and interactive reports (see examples \href{http://cknowledge.org/repo/web.php?wcid=report:request-overview}{1} and \href{http://cKnowledge.org/rpi-crowd-tuning}{2});
\item adding new shared components such as workloads, data sets, tools and platforms;
\item automating AE "at the source" by integrating CK workflows with e.g. \href{https://hotcrp.com/}{HotCRP};
\item standardizing APIs and meta-descriptions of shared components to make them "marketplace-ready";
\item running new ReQuEST competitions for other workloads!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Acknowledgments}

@@

 \item Michaela Blott, Xilinx
 \item Unmesh Bordoloi, General Motors
 \item Ofer Dekel, Microsoft
 \item Maria Girone, CERN openlab
 \item Wayne Graves, ACM
 \item Vinod Grover, NVIDIA
 \item Sumit Gupta, IBM
 \item James Hetherington, Alan Turing Institute
 \item Steve Keckler, NVIDIA
 \item Wei Li, Intel
 \item Colin Osborne, ARM
 \item Andrew Putnam, Microsoft
 \item Boris Shulkin, Magna
 \item Greg Stoner, AMD
 \item Alex Wade, Chan Zuckerberg Initiative
 \item Peng Wu, Huawei
 \item Cliff Young, Google

@@

  \textbf{Optimizing Deep Learning Workloads on ARM GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\

>>>>

Since collapsing all metrics into one to select a single
winner often results in over-engineered solutions, we have
opted instead to select multiple implementations from
a Pareto-frontier, based on their uniqueness or simply
to obtain a reference implementation. The authors of
selected solutions were given an opportunity to share their
insights at the associated \href{http://cknowledge.org/request-cfp-asplos2018.html}{ReQuEST workshop} 
co-located with the 23rd ACM ASPLOS conference.

@@

Most importantly, the community can now access all the above
CK workflows under permissive licenses and continue
collaborating on them via dedicated 
\href{https://github.com/ctuning/ck-request-asplos18-results}{ReQuEST'18 GitHub projects}. 
First, the workflows can be automatically \href{https://github.com/ctuning/ck/wiki/Portable-workflows}{adapted}
to new platforms and environments by either detecting already
installed dependencies (e.g.\ libraries) or rebuilding
dependencies via an integrated \href{http://cKnowledge.org/shared-packages.html}{package manager} supporting
Linux, Windows, MacOS and Android. Second, the workflows can
be customized by swapping in new models, data sets,
frameworks, libraries, and so on. Third, the workflows can be
extended to expose new design and optimization choices (e.g.\ quantization), as well as evaluation metrics (e.g. power
or memory consumption). Finally, the workflows can be used for
collaborative autotuning ("\href{http://cKnowledge.org/rpi-crowd-tuning}{crowd-tuning}") 
to explore huge optimization spaces using devices such as 
\href{https://play.google.com/store/apps/details?id=openscience.crowdsource.video.experiments}{Android phones and tablets}, 
with best solutions being made available to the
community on the \href{http://cKnowledge.org/dnn-crowd-benchmarking-results}{online CK scoreboard}.

@@

Fair competitive benchmarking between different platforms,
frameworks and models is hard work. It requires carefully
considering model equivalence (e.g.\ performing the same mix of
operations), input equivalence (e.g.\  preprocessing the inputs
in the same way), output equivalence (e.g.\ validating the
outputs for each input, not just calculating the usual
aggregate accuracy score), etc. Formalizing the benchmarking
requirements and encapsulating them in shared CK components
(e.g.\ using a framework-independent model representation such
as \href{https://onnx.ai/}{ONNX}) and workflows (e.g.\ for input conversion and output
validation), should help standardize and automate the
benchmarking process.

@@

%\begin{center}\includegraphics{ck-assets/artifacts_automated_dl.jpg}\end{center}

@@

Artifact evaluation may require access to expensive
computational resources (e.g.\ cloud instances with 72-core
servers), proprietary tools (e.g. Intel compilers), and
auxiliary hardware (e.g.\ power meters). Raising the profile
of AE by widely recognizing its benefits and impact should
help us obtain access, licensees and sponsorship from the
industry and funding agencies.

@@

Full experimental evaluation can take many weeks (for example,
when validating accuracy on 50,000 images on a 100 MHz FPGA
board). The AE committee can collaborate with the authors
to determine a minimally useful scope for evaluation which
would still provide insights to the community. The community
can eventually crowdsource full evaluation. In other words,
AE can be "staged" with a quick check that the artifacts are
"functional" before the camera-ready deadline followed by full
evaluation using the ReQuEST methodology. In fact, ReQuEST can
grow into a non-profit service to conferences and journals.
Sponsorship should help attract experienced full-time
evaluators, as well as part-time volunteers, to work
on unifying and evaluating artifacts and workflows.

@@

\item collaborating with the community, our Advisory Board and ACM to address the above issues;
\item using the ReQuEST experience to assist AE at the upcoming \href{http://sysml.cc}{SysML'19} conference;
\item replacing non-representative benchmarks with realistic workloads;
\item creating realistic training sets based on mispredictions shared by the community;
\item improving the benchmarking and co-design methodology, and contributing to emerging benchmarking initiatives such as \href{http://mlperf.org}{MLPerf};
\item collaborating with other competitions such as \href{https://rebootingcomputing.ieee.org/lpirc}{LPIRC}, \href{https://dawn.cs.stanford.edu/benchmark}{DAWNBench} and \href{https://sc18.supercomputing.org/experience/studentssc/student-cluster-competition}{SCC} on developing a common experimental framework;
\item standardizing \href{http://cKnowledge.org/rpi-crowd-tuning}{multi-objective autotuning and co-design workflows};
\item improving and documenting the experimental framework and scoreboard;
\item generating reproducible and interactive reports (see examples \href{http://cknowledge.org/repo/web.php?wcid=report:request-overview}{1} and \href{http://cKnowledge.org/rpi-crowd-tuning}{2});
\item adding new shared components such as workloads, data sets, tools and platforms;
\item automating AE "at the source" by integrating CK workflows with e.g.\ \href{https://hotcrp.com/}{HotCRP};
\item standardizing APIs and meta-descriptions of shared components to make them "marketplace-ready";
\item running new ReQuEST competitions for other workloads!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}

@@

 \item Michaela Blott, Xilinx
 \item Unmesh Bordoloi, General Motors
 \item Ofer Dekel, Microsoft
 \item Maria Girone, CERN openlab
 \item Wayne Graves, ACM
 \item Vinod Grover, NVIDIA
 \item Sumit Gupta, IBM
 \item James Hetherington, Alan Turing Institute
 \item Steve Keckler, NVIDIA
 \item Wei Li, Intel
 \item Colin Osborne, Arm
 \item Andrew Putnam, Microsoft
 \item Boris Shulkin, Magna
 \item Greg Stoner, AMD
 \item Alex Wade, Chan Zuckerberg Initiative
 \item Peng Wu, Huawei
 \item Cliff Young, Google

@@

  \textbf{Optimizing Deep Learning Workloads on Arm GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
